---
title: "assign4"
output: html_notebook
---


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

```{r}
library(lubridate)
library(stringr)
library(htmlwidgets)
library(RVerbalExpressions)

# install.packages("devtools")
# devtools::install_github("VerbalExpressions/RVerbalExpressions")
```

# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 


```{r generate first day}
ymd("2019-01-01") + months(0:11)
```

Write a function that given your birthday (as a date), returns how old you are in years.
```{r how old you are}
get_age<-function(birthday){
  as.numeric(today()-ymd(birthday))%/%365
}
get_age('1998-02-28')
```





Write a function that given your birthday, returns the day of the week you were born on. 


```{r weekday}
get_weekday<-function(birthday){
  wday(ymd(birthday),label=T)
  # weekdays(ymd(birthday))
}

get_weekday('1998-02-28')
```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)


```{r import data}
stringr::words
```


```{r more than 7}
str_view(words, "\\w{7,}", match = TRUE)
morethan7 <- rx() %>%
  rx_word_char() %>%
  rx_repeat_previous(7) %>%
  rx_anything()
morethan7
str_view(words, morethan7, match = TRUE)
```

## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)

```{r only consonants}
words[str_detect(words, "^[^aeiou]+$") ]
consonants_only <- rx() %>%
  rx_start_of_line() %>%
  rx_something_but("aeiou") %>%
  rx_end_of_line()
consonants_only
words[str_detect(words, consonants_only) ]
```

Empirically verify the rule “i before e except after c”.


```{r  “i before e except after c”}
words[str_detect(words, "cie")]
cie <- rx() %>%
  rx_find("cie")
cie
words[str_detect(words, cie)]
```
*answer* The rule is not always true. "science" and "society" disobey the rule.




Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.


```{r telephone number}
tele <- rx() %>%
  rx_start_of_line() %>%
  rx_maybe("(") %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>%
  rx_maybe(")") %>%
  rx_any_of(" .-") %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>%
  rx_any_of(" .-") %>%
  rx_digit() %>%
  rx_repeat_previous(4) %>%
  rx_end_of_line() 
tele
phonenum <- c("(615) 397-0128","(615) 481.1536","(abc) 777 8888")
phonenum[str_detect(phonenum, "^(\\()?[0-9]{3}(\\))?[ -\\.][0-9]{3}[ -\\.][0-9]{4}$")]
phonenum[str_detect(phonenum, tele)]
```




# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

